---
title: "Mini-Project 2: Adventure 1"
author: Anael Kuperwajs Cohen, Juliet Kelson
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---


```{r}
library(dplyr)
library(ggplot2)
library(caret)
library(stringr)
library(tidyverse)
library(quanteda)
```


\
\



## Part 1: Process the data

```{r}
buzzfeed <- read.csv("https://www.macalester.edu/~ajohns24/data/buzzfeed.csv")

buzzfeed <- buzzfeed %>% 
  mutate(title = as.character(title),
         text = as.character(text),
         url = as.character(url))

'%!in%' <- function(x, y)!('%in%'(x,y))
```



### New predictors

Our new predictors will be:

1. Lexical density (unique words/total words)
2. Flesch–Kincaid grade level
3. Primary sentiment
4. Secondary sentiment
5. ! ratio (to . ?)
6. Author Count
7. 
8. Word count
9. Sentence Count
10. Syllables
11.
12. News Source
13. Strength of primary sentiment
14. Strength of secondary sentiment
15. Count of upper-case words

8.
```{r}
buzzfeed <- buzzfeed %>% 
  mutate(total_words = str_count(text, " ") + 1)
```

15.
```{r}
buzzfeed <- buzzfeed %>% 
  mutate(total_upper_case_words = str_count(text, "\\b[A-Z]{2,}\\b"))
```

6. FIX THIS
```{r}
buzzfeed <- buzzfeed %>%
  mutate(authors = gsub("View All Posts,", "", authors)) %>% 
  # Abc News,", "Cnn National Politics Reporter,", "Cnn Pentagon Correspondent,", "Latest Posts,", "Cnn White House Producer,", "Cnn Senior Congressional Producer,"), "", authors)) %>% 
  mutate(author_count = str_count(authors, ",") + 1) %>% 
  mutate(author_count = if_else(author_count == 0, 1, author_count))
```

Trying to get rid of wrong authors:
buzzfeed <- buzzfeed %>% 
  filter(author %!in% c("View All Posts", "Abc News", "Cnn National Politics Reporter", "Cnn Pentagon Correspondent", "Latest Posts", "Cnn White House Producer", "Cnn Senior Congressional Producer"))


10.
```{r}
buzzfeed <- buzzfeed %>% 
  mutate(syllables = nsyllable(text))
```

9.
```{r}
buzzfeed <- buzzfeed %>% 
  mutate(total_sentences = nsentence(text))
```


\
\
\
\
\
\



## Part 2: Analyze


\
\
\
\
\
\



## Part 3: Summarize




\
\
\
\
\
\



## Part 4: Contributions

