---
title: "Mini-Project 2: Adventure 1"
author: Anael Kuperwajs Cohen, Juliet Kelson
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---


```{r}
library(dplyr)
library(ggplot2)
library(caret)
library(stringr)
library(tidyverse)
```


\
\



## Part 1: Process the data

```{r}
buzzfeed <- read.csv("https://www.macalester.edu/~ajohns24/data/buzzfeed.csv")

buzzfeed <- buzzfeed %>% 
  mutate(title = as.character(title),
         text = as.character(text),
         url = as.character(url))
```



### New predictors

Our new predictors will be:

1. Lexical density (unique words/total words)
2. Flesch–Kincaid grade level
3. Primary sentiment
4. Secondary sentiment
5. ! ratio (to . ?)
6. Author
7. Date
8. Word count
9. Sentence Count
10. Syllables
11. Location
12. News Source
13. Strength of primary sentiment
14. Strength of secondary sentiment
15. Count of upper-case words

8.
```{r}
buzzfeed <- buzzfeed %>% 
  mutate(total_words = str_count(text, " ") + 1)
```

15.
```{r}
buzzfeed <- buzzfeed %>% 
  mutate(total_upper_case_words = str_count(text, "\\b[A-Z]{2,}\\b"))
```

6.
```{r}
buzzfeed <- buzzfeed %>% 
  gather() %>% 
  spread()
```


\
\
\
\
\
\



## Part 2: Analyze


\
\
\
\
\
\



## Part 3: Summarize




\
\
\
\
\
\



## Part 4: Contributions

